---
title: "HackerRank R"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1.
Given an integer, n, perform the following conditional actions:

If n is odd, print Weird
If n is even and in the inclusive range of 2 to 5, print Not Weird
If n is even and in the inclusive range of 6 to 20, print Weird
If n is even and greater than 20, print Not Weird


```{r }
f <- function(n) {
  if (n%%2 == 1) {
    print("Weird")
  } else 
      if (n%%2 == 0 & n>=2 & n<=5) {
        print("Not Weird")
  }
      else if (n%%2 == 0 & n>=6 & n<=20) {
      print("Weird")
    }
      else if (n%%2 == 0 & n>20) {
       print("Not Weird")
  }
      else  {
       print("Wrong")
  }
  
}

f(8)
```

## 2

The provided code stub reads two integers from STDIN, a and b. 
  Add code to print three lines where:
  The first line contains the sum of the two numbers.
  The second line contains the difference of the two numbers (first  second).
  The third line contains the product of the two numbers.

```{r }
f2 <- function(a, b) {
  print(a + b)
  print(a - b)
  print(a * b)
}

f2(3, 5)
```

## 3

The provided code stub reads two integers, a and b, from STDIN.
Add logic to print two lines. The first line should contain the result of integer division,  a// b. The second line should contain the result of float division, a / b.
No rounding or formatting is necessary.

```{r}
f3 <- function(a, b) {
  print(trunc(a/b))
  print(a/b)
}

f3(3, 5)
```

## 4

The provided code stub reads and integer, n, from STDIN. For all non-negative integers i < n, print i^2.

```{r}
f4 <- function(n) {
  for (i in 0:n){
     print(i*i)
    }
}

f4(5)
```

## 5

Given a year, determine whether it is a leap year. If it is a leap year, return the Boolean True, otherwise return False.

Note that the code stub provided reads from STDIN and passes arguments to the is_leap function. It is only necessary to complete the is_leap function.

```{r}
f5 <- function(year) {
  if (year %% 4 == 0){
    "True"
  } else {
     if (year %% 100 == 0 & year %% 400 == 0) {
      "True"
     }
     else {
       "False"
     }
  }
}

f5(1990)
```

## 6

The included code stub will read an integer, n, from STDIN. Without using any string methods, try to print the following:

123...n

Note that "..." represents the consecutive values in between.

```{r}
f6 <- function(n)  {
  for (i in 1:n) {
    cat(paste(i,""))
  }
}

f6(3)
```




